NumPy---Array Programming in Python

### 2020-01-11 body.tex
Minor edits to interop section

NumPy's API has become ubiquitous in scientific computation, but NumPy itself
can never hope to satisfy every single specialized need of the community.
The advent of new technologies, such as GPUs, create opportunities that should be
exploited, but are out of scope for NumPy development.
Still, the widespread adoption of the NumPy API is valuable, as it lowers the
barrier to entry and provides stability to the community.
What can NumPy do to support the use of its API without blocking innovation?
We believe that improving interoperability by having NumPy be a central
coordinator among array objects is a good way to balance stability while
supporting growth of a larger surrounding ecosystem of specialized solutions
and new tools.
Primarily, there exist two types of Python array objects: subclasses of NumPy
arrays, and arrays that mimic NumPy arrays but are fundamentally different.

@@

To facilitate \emph{interoperability}, the NumPy team is defining so-called
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions.
NumPy, in turn, dispatches operations to the originating library, as required.

>>>>

NumPy's API has become ubiquitous in scientific computation, but NumPy itself
can never hope to satisfy every single specialized need of the community.
The advent of new technologies, such as GPUs, create opportunities that should be
exploited, but are out of scope for NumPy development.
Still, the widespread adoption of the NumPy API is valuable, as it lowers the
barrier to entry and provides the wider community with a stable array programming interface.
What can NumPy do to support the use of its API without blocking innovation?
We believe that having NumPy as a central point of coordination between array objects can improve interoperability while
supporting growth of a larger surrounding ecosystem of specialized solutions
and new tools.
Primarily, there exist two types of Python array objects: subclasses of NumPy
arrays, and arrays that mimic NumPy arrays but are fundamentally different.

@@

To facilitate \emph{interoperability}, the NumPy team is defining so-called
``protocols'' (or contracts of operation), that allow for these arrays to be
passed to NumPy functions.
NumPy, in turn, dispatches operations to the originating library, as required.  Early versions of these protocols have been successfully deployed.
